### 2024-01-01 chapters/main-contributions.tex
Polish background

\contribitem{chp:paper-brief}
In this chapter, we present a comprehensive overview of unsupervised neural representation learning for speech. Previous research is categorized into self"=supervised methods and probabilistic latent variable models and described in a common notation. This description assists in developing a model taxonomy that shapes a discussion of the models' representational power, the associated learning strategies, and the methods used to evaluate them. The discussion points to interesting avenues of future research. 
An extended version of this overview paper that focuses exclusively on self"=supervised methods was also published as part of the project \ref{enumerate: paper-review} \parencite{mohamed_selfsupervised_2022} and this paper is included in \cref{app:paper-review} for reference.

>>>>

\contribitem{chp:paper-brief}
In this chapter, we present a comprehensive overview of unsupervised neural representation learning for speech. Previous research is categorized into self"=supervised methods and probabilistic latent variable models and described in a common notation. This description assists in developing a model taxonomy that shapes a discussion of the models' representational power, the associated learning strategies, and the methods used to evaluate them. The discussion points to interesting avenues of future research. 
An extended version of this overview paper that focuses exclusively on self"=supervised methods was also published as part of the project \ref{enumerate: paper-review} \parencite{mohamed_selfsupervised_2022} and is included in \cref{app:paper-review} for reference.
